---
title: "Tutorial_BayModDSGD"
author: "Qicheng Zhao"
date: "2025-02-08"
output: html_document
---

The following provides a tutorial for the \textbf{BayModDSGD} package. After importing the package, we will examine the toy dataset as shown below:

```{r}
library(BayModDSGD)
data(toy)
head(toy)
```
The dataset will be partitioned into two distinct components: a matrix X comprising covariates (consisting of log-transformed gene expression counts and spatial coordinates for each location) and a response vector Y containing the disease status indicators.
```{r}
x <- toy[, c("x.V1", "x.V2", "x.V3", "x.x_coord", "x.y_coord")]  
y <- toy$y  
```


To demonstrate the workflow of our method, we present the step-by-step procedure using this dataset. Initially, we perform missing data imputation under the assumption of an ignorable missing data mechanism.

```{r}
missing_indices <- sample(length(y), 10)# select 10 values to let them become missing values
y[missing_indices] <- NA
coord<-as.matrix(toy[, c("x.x_coord", "x.y_coord")])  #To retrieve the spatial information for each spot
imputed_mean<-missing_imputation(y,coord)[missing_indices]
y[missing_indices]<-rbinom(10,1,imputed_mean) # imputed the missing values by the corresponding estimated mean
```

The function \textit{missing_imputation} performs missing data imputation and returns a list of estimated means for each missing value. These estimated means are then used to impute the dataset.  

Subsequently, the \textit{dsgd_single} function is employed to conduct the analysis. The \textit{list_y} parameter represents a vector containing disease status information for each spatial location or cell, while \textit{matrix_x} includes both genetic and spatial data corresponding to each observation.

```{r}
dsgd_single(list_y=y,matrix_x=x) # since the last two columns in x is the spatial information
```

Next, we present an example involving multiple samples from individuals, utilizing an alternative toy dataset referred to as 'toy2'.

```{r}
data(toy2)
head(toy2)
x <- toy2[, c("x.V1", "x.V2", "x.V3", "x.x_coord", "x.y_coord")]  
y <- toy2$y  
label<- toy2$label
```

The fundamental structure remains unchanged, with the only distinction being the addition of a new column, 'label,' which differentiates the data slices. The following function can then be executed to fit the model.

```{r}
dsgd_multiple(y,x,label)
```
Notice: This package is currently under development, and further refinements will be made in subsequent updates.
